---
title: "Project title"
subtitle: "Proposal"
format: html
editor: visual
---

```{r}
#| label: load-pkgs
#| message: false

library(tidyverse)
```

# Data 1

## Introduction and data

-   Identify the source of the data.

    -   This data is from the CORGIS Dataset Project.

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

    -   It was collected in 2016.

    -   It compiled 2015 Forbes World's Billionaires list shows a record number of billionaires in the world (1,826) while adding detailed information on the individuals listed.

-   Write a brief description of the observations.

    -   The observation includes the personal information of billionaire such as their name, gender, demographics, and citizenship. It also include their company information such as name, industry, inherited, and founder.

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

    -   What is the relationship between wealth worth and industry among the billionaires in North America?

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

    -   This research question will help us understand how the industry a billionaire works in affects their net worth in North America. We will look at all the different industries and see how those different industries lead to different net worths. Ultimately the goal is to find a trend that can help us determine which industries are more successful than others. We predict that some industries such as technology-computer, consumer, and money management will have higher rates of producing billionaires than others.

-   Identify the types of variables in your research question. Categorical? Quantitative?

    -   The variable of industry (wealth.how.industry) is categorical and the variable of net worth (wealth.worth) is quantitative.

## Literature

-   Find one published credible article on the topic you are interested in researching.

    -   https://businesstech.co.za/news/business/576098/the-job-sectors-where-most-billionaires-make-their-money/?\_\_cf_chl_tk=Ukf90omcnnDfbwhqcd6GDNpECHPyadqZsZk1cgA10R4-1678392097-0-gaNycGzNCxA

-   Provide a one paragraph summary about the article.

    -   The article presents findings from a study by UBS and PwC on the sectors where most billionaires made their money. The study analyzed the wealth of 2,000 billionaires worldwide and found that the top sectors where billionaires made their wealth are finance and investments, technology, manufacturing, real estate, and fashion and retail. Finance and investments had the most billionaires with 267, followed by technology with 221, manufacturing with 215, real estate with 163, and fashion and retail with 135. The study underscores the diversity of the sectors in which billionaires can generate wealth.

-   In 1-2 sentences, explain how your research question builds on / is different than the article you have cited.

    -   This article presents findings using billionaires from all over the world. In contrast, our research question is only exploring billionaires within North America. This will allow us to compare how the relationship between billionaires in North America and their industries differ from billionaires worldwide.

## Glimpse of data

```{r}
#| label: load-data-1
billionaires <- read_csv("data/billionaires.csv")

head(billionaires)
glimpse(billionaires)


```

# Data 2

## Introduction and data

-   Identify the source of the data.

    -   This data is from Washington Post.

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

    -   It was originally collected in 2015, when the Washington Post was trying to compile a database of every fatal shooting in the United States by a police officer in the line of duty since Jan.1 2015.

    -   It was collected by culling local news reports, law enforcement websites and social media, and by monitoring independent database such as Killed by Police and Fatal Encounters.

-   Write a brief description of the observations.

    -   The data contains basic victim information such as name, age gender, race, and whether the victim is armed or not. It also contains information about the shooting case such as the date, location city, location state. Plus more information about the police officer like body camera status, armed or not.

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

    -   

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

    -   

-   Identify the types of variables in your research question. Categorical? Quantitative?

    -   

## Literature

-   Find one published credible article on the topic you are interested in researching.

    -   

-   Provide a one paragraph summary about the article.

    -   

-   In 1-2 sentences, explain how your research question builds on / is different than the article you have cited.

    -   

## Glimpse of data

```{r}
#| label: load-data-2


police_shootings <- read_csv("data/police_shootings.csv")

head(police_shootings)


```

# Data 3

## Introduction and data

-   Identify the source of the data.

    -   Data was collected from individual states as part of the NSDUH study.

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

    -   It was collected in 2021.

    -   This data collected from Substance Abuse and Mental Health Services Administration (SAMHSA)'s public online data analysis system (PDAS).

-   Write a brief description of the observations.

    -   This dataset is about substance abuse (cigarettes, marijuana, cocaine, alcohol) among different age groups and states. Data was collected from individual states as part of the NSDUH study. The data ranges from 2002 to 2018. Both totals (in thousands of people) and rates (as a percentage of the population) are given.

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

    -   From 2002 to 2018, how does drug use by population between alcohol, cocaine, tobacco, and marijuana vary by year?

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

    -   Our research topic is understanding the curve and decrease/increase of certain drug use on the population from years 2002 to 2018 by year. We will compare the differing numbers of drug uses by year from 2002-2018, understanding the general trend of the data. From 2002-2018, there is likely to be an increase of substance users.

-   Identify the types of variables in your research question. Categorical? Quantitative?

    -   Our data uses mostly quantitative variables to check the numbers of usage of the differing substances from 2002-2018.

        ## Literature

-   Find one published credible article on the topic you are interested in researching.

-   **Towards explaining time trends in adolescents' alcohol use: a multilevel analysis of Swedish data from 1988 to 2011**

    <https://doi.org/10.1093/eurpub/ckz023>

    Junhwan Kim, Brittany E Evans, Curt Hagquist, Towards explaining time trends in adolescents' alcohol use: a multilevel analysis of Swedish data from 1988 to 2011, *European Journal of Public Health*, Volume 29, Issue 4, August 2019, Pages 729--735

-   Provide a one paragraph summary about the article.

    -   The authors use data from repeated cross-sectional surveys of Swedish high school students, analyzing the data using a multilevel approach to explore both individual-level and contextual-level predictors of alcohol use.The study found that the prevalence of alcohol use among Swedish adolescents decreased over time, and that this trend was particularly pronounced among girls. Individual-level factors such as gender, age, and parental education were found to be strongly associated with alcohol use, as were contextual-level factors such as school-level socioeconomic status and alcohol availability in the community.

-   In 1-2 sentences, explain how your research question builds on / is different than the article you have cited.

    -   In our data, we also will be comparing the trend of alcohol/drug usage over time and possibly predicting the contextual reasons behind it. However, we will not be using data from the US, not Sweden, and we will be looking across all age groups.

## Glimpse of data

```{r}
#| label: load-data-3

drugs <- read_csv("data/drugs.csv")

head(drugs)
```
