---
title: "Project title"
subtitle: "Proposal"
format: html
editor: visual
---

```{r}
#| label: load-pkgs
#| message: false

library(tidyverse)
```

# Data 1

## Introduction and data

-   Identify the source of the data.

    -   This data is from the CORGIS Dataset Project.

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

    -   It was collected in 2016.

    -   It compiled 2015 Forbes World\'s Billionaires list shows a record number of billionaires in the world (1,826) while adding detailed information on the individuals listed.

-   Write a brief description of the observations.

    -   The observation includes the personal information of billionaire such as their name, gender, demographics, and citizenship. It also include their company information such as name, industry, inherited, and founder.

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

    -   

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

    -   

-   Identify the types of variables in your research question. Categorical? Quantitative?

    -   

## Literature

-   Find one published credible article on the topic you are interested in researching.

    -   

-   Provide a one paragraph summary about the article.

    -   

-   In 1-2 sentences, explain how your research question builds on / is different than the article you have cited.

    -   

## Glimpse of data

```{r}
#| label: load-data-1
billionaires <- read_csv("data/billionaires.csv")

head(billionaires)
glimpse(billionaires)


```

# Data 2

## Introduction and data

-   Identify the source of the data.

    -   This data is from Washington Post.

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

    -   It was originally collected in 2015, when the Washington Post was trying to compile a database of every fatal shooting in the United States by a police officer in the line of duty since Jan.1 2015.

    -   It was collected by culling local news reports, law enforcement websites and social media, and by monitoring independent database such as Killed by Police and Fatal Encounters.

-   Write a brief description of the observations.

    -   The data contains basic victim information such as name, age gender, race, and whether the victim is armed or not. It also contains information about the shooting case such as the date, location city, location state. Plus more information about the police officer like body camera status, armed or not.

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

    -   

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

    -   

-   Identify the types of variables in your research question. Categorical? Quantitative?

    -   

## Literature

-   Find one published credible article on the topic you are interested in researching.

    -   

-   Provide a one paragraph summary about the article.

    -   

-   In 1-2 sentences, explain how your research question builds on / is different than the article you have cited.

    -   

## Glimpse of data

```{r}
#| label: load-data-2


police_shootings <- read_csv("data/police_shootings.csv")

head(police_shootings)


```

# Data 3

## Introduction and data

-   Identify the source of the data.

    -   Data was collected from individual states as part of the NSDUH study.

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

    -   It was collected in 2021.

    -   This data collected from Substance Abuse and Mental Health Services Administration (SAMHSA)'s public online data analysis system (PDAS).

-   Write a brief description of the observations.

    -   This dataset is about substance abuse (cigarettes, marijuana, cocaine, alcohol) among different age groups and states. Data was collected from individual states as part of the NSDUH study. The data ranges from 2002 to 2018. Both totals (in thousands of people) and rates (as a percentage of the population) are given.

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

    -   

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

    -   

-   Identify the types of variables in your research question. Categorical? Quantitative?

    -   

## Literature

-   Find one published credible article on the topic you are interested in researching.

    -   

-   Provide a one paragraph summary about the article.

    -   

-   In 1-2 sentences, explain how your research question builds on / is different than the article you have cited.

    -   

## Glimpse of data

```{r}
#| label: load-data-3

drugs <- read_csv("data/drugs.csv")

head(drugs)
```
