---
title: "Wanna be successful? Here's how!"
subtitle: "A statistical analysis regarding the success of different industries based on the billionaires within each of them"
format: html
editor: visual
execute:
  echo: false
---

#### Introduction and data

Our topic focus on the dataset "Billionaires" (2016), which contains information on the Billionaires in the world in 1996, 2001, 2014. The dataset involves information on each billionaire such as their country, wealth worth, wealth type, industry, etc. Using some of these variables, we came up with a question that helps us gather more insight on the wealth world, which is helpful for those who are deciding which industry to enter in North America, and how that changes over time.

Research Question and Hypothesis:

-   How has the relationship between wealth worth and industry among billionaires changed in North America as time goes on?

Based on our prior background knowledge, we predict that the number of billionaires involved in the industry of technology-computer will increase as time goes by because technology is an industry that is growing rapidly. We believe that the consumer industry may increase as well, and that the some of the more popular industries in 1996 might decrease in the number of billionaires as time passes. More broadly speaking, we hypothesize that the overall number of billionaires will increase, and therefore each industry will have a higher number of billionaires as time progresses, simply because there is more money in the world. We also predict that the average wealth worth will increase among all billionaires across all industries as time goes.

(In this dataset, wealth worth refers to the net worth of an individual in billions of US dollars. It is measured by taking into account the individual's assets, including real estate, investments, and other sources of income, and subtracting any liabilities, such as debts or mortgages. The resulting net worth is then converted into billions of US dollars for ease of comparison across the dataset.)

The data was from the CORGIS Dataset Project, collected by Ryan Whitcombwas in 1996, 2001, and 2014. \[1\] We are using data from all three years to see how the wealth industries have changed over time by comparing data about the wealth industries from each provided year. It compiled Forbes World's Billionaires list and shows a record number of billionaires in the world while adding detailed information on the individuals listed. The relevant variables include the year, wealth worth, industry, and their continent. In total, the data set has 22 columns and 2614 observations. We are focusing our studies on the continent North America, to explore the relationship between billionaires and wealth worth in this area in particular over time.

To help us answer our research question, we looked at the Businesstech article, "The job sectors where billionaires make their money" presents findings from a study by UBS and PwC on the sectors where most billionaires succeeded. \[2\] The study analyzed the wealth of 2,000 billionaires worldwide and found that the top sectors where billionaires made their wealth are finance and investments, technology, manufacturing, real estate, and fashion and retail. Finance and investments had the most billionaires with 267, followed by technology with 221, manufacturing with 215, real estate with 163, and fashion and retail with 135. The study underscores the diversity of the sectors in which billionaires can generate wealth.

This article presents findings using billionaires from all over the world, whereas our research question is only exploring billionaires within North America. This will allow us to compare how the relationship between billionaires in North America and their industries differ from billionaires worldwide. Additionally, the article notes that technology is a top sector for billionaires to make most of their money, which reflects our hypothesis that technology will reflect the greatest increase in billionaires, as it is a sector that is growing rapidly.

#### Methodology

Our methodology involves multiple components. First, we used data wrangling to make this dataset relevant to our question. We selected these specific columns from the data frame: year, name, wealth.worth in billions, wealth.how.industry, location.region, and location.citizenship. We renamed the column "wealth.worth in billions" to "wealth.worth.billions", and created a new column called "continent" using the mutate function (there was only location region before). This allowed us to put the data from Mexico (from location region Latin America) with the data from the location region North America because it is officially a part of North America. Next, we found the number of billionaires per industry for each of the three years (1996, 2001, and 2014). Using this information, we can compare them and see how the number of billionaires has changed over time. Of course, this does not tell us anything about quantity of wealth, so in addition to the number of billionaires alone, we thought it would be beneficial to find the average wealth worth of the billionaires in each industry. We did this for all three years, and created a visualization to show how mean wealth worth has changed. From this, we can see the growth of certain industries as well as the diminish of others. Lastly, we conducted a hypothesis test for the general mean wealth worth, first for 2001 and 2014, and then for 1996 and 2001. We used the Central Limit Theorem (CLT) in our data analysis because there were sample sizes greater than 30. A two-sample t-test was conducted to compare the change in mean wealth worth per billionaire across industries over time. These hypothesis tests tell us whether there was a true, significant change in mean wealth worth between those years. An $\alpha$ value of 0.05 was used. This is for the general wealth worth, but could be done for the specific industries as well.

```{r}
#| label: load-pkgs
#| message: false

library(tidyverse)
library(tidymodels)
```

```{r}
#| label: load-data-2014
#| fig-width: 20
#| message: false

#Load data
billionaires <- read_csv("data/billionaires.csv")

df_1 <- billionaires|>
  dplyr::select(year, name, "wealth.worth in billions", wealth.how.industry, location.region, location.citizenship)|>
  rename_with(~'wealth.worth.billions', "wealth.worth in billions")|>
  mutate(continent = case_when(
    location.region == "Latin America" & location.citizenship == "Mexico" ~ "North America",
    TRUE ~ location.region
  ))
```

```{r}
#| label: count-billionaires-per-year

df_1996 <- df_1 |>
  filter(year == 1996, wealth.how.industry != 0) |>
  group_by(wealth.how.industry) |>
  summarize(num_billionaires = n()) |>
  arrange(desc(num_billionaires))
df_1996 

df_2001 <- df_1  |>
  filter(year == 2001, wealth.how.industry != 0) |>
  group_by(wealth.how.industry) |>
  summarize(num_billionaires = n()) |>
  arrange(desc(num_billionaires))
df_2001

df_2014 <- df_1  |>
  filter(year == 2014, wealth.how.industry != 0) |>
  group_by(wealth.how.industry) |>
  summarize(num_billionaires = n()) |>
  arrange(desc(num_billionaires))
df_2014



```

```{r}
#| label: mean_wealth_1996

#Create data frame for mean wealth in 1996
df_1996 <- df_1 |>
  filter(year == 1996) |>
  filter(wealth.how.industry != 0) |>
  filter(location.region == "North America") |>
  group_by(wealth.how.industry) |>
  summarize(mean_wealth = mean(wealth.worth.billions, na.rm = T)) |>
  mutate(year = if_else(mean_wealth != 0, 1996, 0))
  

```

```{r}
#| label: mean_wealth_2001

#Create data frame for mean wealth in 2001
df_2001 <- df_1 |>
  filter(year == 2001) |>
  filter(wealth.how.industry != 0) |>
  filter(location.region == "North America") |>
  group_by(wealth.how.industry) |>
  summarize(mean_wealth = mean(wealth.worth.billions, na.rm = T))|>
  mutate(year = if_else(mean_wealth != 0, 2001, 0))
```

```{r}
#| label: mean_wealth_2014

#Create data frame for mean wealth in 2014
df_2014 <- df_1 |>
  filter(year == 2014) |>
  filter(wealth.how.industry != 0) |>
  filter(location.region == "North America") |>
  group_by(wealth.how.industry) |>
  summarize(mean_wealth = mean(wealth.worth.billions, na.rm = T))|>
  mutate(year = if_else(mean_wealth != 0, 2014, 0))
```

```{r}
#| label: visualization-mean-wealth
#| fig-width: 10
#| fig-height: 8

#Assign color to the legend
distinct_colors <- c("#E6194B", "#3CB44B", "#FFE119", "#0082C8", "#F58231", "#911EB4", "#46F0F0", 
                     "#F032E6", "#D2F53C", "#008080", "#AA6E28", "#800000", "#000080", "#808000",
                     "#E6BEFF", "#AAFFC3", "black")

#Combine data frame together
df_rbind <- rbind(df_1996, df_2001)
df_rbind <- rbind(df_rbind, df_2014)

#visualize the graph
df_rbind |>
  ggplot(
    aes(x = year,
        y = mean_wealth,
        color = wealth.how.industry))+
  geom_line(size = 1) +
  geom_point() +
  scale_x_continuous(limits = c(1996, 2014.5), breaks = c(1996, 2001, 2014)) +
  theme_classic()+
  scale_color_manual(values = distinct_colors) +
  labs( title = "Mean Wealth Worth in Billions By Year Per Industry",
    x = "Year",
    y = "Mean Wealth Worth in Billions ($)",
    color = "Industry type"
  )

```

```{r}
#| label: data-frames-for-hypothesis-testing
#| echo: false
#| warning: false
df_2014 <- df_1|>
  filter(year == "2014")|>
  dplyr::select(wealth.worth.billions, wealth.how.industry)


df_2001<- df_1|>
  filter(year  == "2001")|>
  dplyr::select(wealth.worth.billions, wealth.how.industry)

df_1996<- df_1|>
  filter(year  == "1996")|>
  dplyr::select(wealth.worth.billions, wealth.how.industry)

```

$H_{0}= x-y \le 0$

$H_{a}= x - y > 0$

$\alpha = 0.05$

x being the mean wealth worth per billionaire in 2014, and y being the mean wealth worth per billionaire in 2001.

The null hypothesis states that from 2001 to 2014, the average wealth worth has not changed or has decreased.

The alternative hypothesis states that from 2001 to 2014, the average wealth worth has increased.

```{r}
#| label: preparation-for-hypothesis-test
#| echo: false
#| warning: false
df_2014mean<- df_2014|>
  group_by(wealth.how.industry) |>
  summarize(mean_wealth = mean(wealth.worth.billions, na.rm = T))

df_2001mean<- df_2001|>
  group_by(wealth.how.industry) |>
  summarize(mean_wealth = mean(wealth.worth.billions, na.rm = T))


df2001mean_wealth_combined <- mean(df_2001mean$mean_wealth, na.rm = TRUE)

df2014mean_wealth_combined <- mean(df_2014mean$mean_wealth, na.rm = TRUE)

estimate <-3.429636 - 2.568625
```

```{r}
#| label: hypothesis-test
#| echo: false
#| warning: false
df_1|>
  filter(!is.na(wealth.worth.billions), year == 2014)|>
  count(wealth.how.industry)

df_1|>
  filter(!is.na(wealth.worth.billions), year == 2001)|>
  count(wealth.how.industry)

sd1 <- df_2014|>
  summarize(sd_a = sd(wealth.worth.billions, na.rm = T)) |>
  as.numeric()
n1 <-1653

sd2 <- df_2001|>
  summarize(sd_a = sd(wealth.worth.billions, na.rm = T)) |>
  as.numeric()
n2 <-538

tscore <- (estimate - 0) / sqrt(((sd1^2)/n1) + ((sd2^2)/n2))
pt(tscore, df= 1171.399 , lower.tail = F)
```

$H_{0}= x-y \le 0$

$H_{a}= x - y > 0$

$\alpha = 0.05$

x being the mean wealth worth per billionaire in 2001, and y being the mean wealth worth per billionaire in 1996.

The null hypothesis states that from 1996 to 2001, the average wealth worth has not changed or has decreased.

The alternative hypothesis states that from 1996 to 2001, the average wealth worth has increased.

```{r}
#| label: preparing-for-hypothesis-test-2
#| echo: false
#| warning: false
df_1996mean<- df_1996|>
  group_by(wealth.how.industry) |>
  summarize(mean_wealth = mean(wealth.worth.billions, na.rm = T))

df1996mean_wealth_combined <- mean(df_1996mean$mean_wealth, na.rm = TRUE)

estimate1<- 2.568625 - 2.335113
```

```{r}
#| label: hypothesis-test-2 
#| echo: false
#| warning: false
df_1|>
  filter(!is.na(wealth.worth.billions), year == 2001)|>
  count(wealth.how.industry)

df_1|>
  filter(!is.na(wealth.worth.billions), year == 1996)|>
  count(wealth.how.industry)

sd3 <- df_2001|>
  summarize(sd_a = sd(wealth.worth.billions, na.rm = T)) |>
  as.numeric()
n3 <-538

sd4 <- df_1996|>
  summarize(sd_a = sd(wealth.worth.billions, na.rm = T)) |>
  as.numeric()
n4 <-423

tscore <- (estimate1 - 0) / sqrt(((sd3^2)/n3) + ((sd4^2)/n4))
pt(tscore, df= 793.3797 , lower.tail = F)


```

#### Results

From our visualizations and tests in the methodology section, we can draw conclusions that help answer our research question of how the relationship between wealth worth and industry among billionaires has changed in North America as time goes on.

From the visualizations, we found that over the years, there has been a noticeable rise in the number of billionaires across most industries, along with a significant increase in their average wealth worth in billions. Among all industries, the technology computer industry has consistently shown the highest mean wealth worth over the three years. However, the greatest increase in mean wealth worth was observed in the diversified financial industry. It is also worth noting that the services industry was removed from the dataset in 2001, and this shows a decline in its overall success and profitability. On the other hand, the venture capital industry was added to the dataset in 2001, which shows its increase in overall success and profitability. Furthermore, the private equity/leveraged buyout industry experienced a dip in its graph (decrease in mean wealth worth), followed by an increase in later years.

However, our hypothesis test does not fully agree that the mean general wealth worth has been consistently increasing. For the first dataset comparison (2001 vs. 2014), it led to rejection of the null hypothesis because the p-value of 0.0001527831 is less than the alpha value of 0.05, This indicates that there is an increase in mean wealth worth. However, the second comparison (1996 vs. 2001) resulted in a p-value of 0.1394406, which is greater than 0.05. Thus we accept the null hypothesis, and there is not conclusive evidence of an increase due to potential sample size differences and smaller increases during that time period. It is important to note that only the upper tail of the distribution was considered due to the alternative hypothesis testing greater than 0. Thus, our analysis does not support the conclusion that mean wealth worth per billionaire increased from 1996 to 2001.

#### Discussion

**Summary:**

From our research project, we learned that most industries grew due to the fact that both the number of billionaires within the industry increased as well as the mean wealth worth (not taking inflation into account though; will be discussed in next section). Changes in the dataset, such as the removal or addition of industries, can reflect broader trends in the overall success and profitability of certain sectors. The hypothesis test showed a significant increase in mean wealth worth per billionaire from 2001-2014 but not from 1996-2001. Keep in mind that this test was a generalization of total mean wealth worth for each year NOT considering industry. Future research can include more detailed hypothesis testing, such as conducting one for each of the industry. This leads into the next part of the discussion about limitations and future research.

**Limitations and future research:**

We have 3 main limitations that we would like to include in this discussion.

1.  Inflation: We did not consider the effects of inflation. Our model were based on the exact wealth worth in billion dollars in those years. We also anticipated that inflation can have a significant impact on wealth worth since 1996. We'd recommend future research does take in effect of inflation into account.

2.  Heritage: Some billionaires in our data set were inherited from their parents. Therefore their data may not accurately reflect their industry type.

3.  Data from 1996, 2001, and 2014 are not enough for a comprehensive analysis. In order to form a more precise and accurate model, we'd recommend to include more data from not just 3 years but every consecutive year from the beginning to the end so that a better trend can be presented.

**Citation and Reference**

\[1\] "Billionaires CSV File" from the CORGIS Dataset Project. By Ryan Whitcomb, Version 2.0.0, created on 5/17/2016.

\[2\] Businesstech. (2022, April 18). The job sectors where most billionaires make their money. Retrieved March 9, 2023, from<https://businesstech.co.za/news/business/576098/the-job-sectors-where-most-billionaires-make-their-money/>
