---
title: "Wanna be rich? Here's how!"
subtitle: "A statistical analysis regarding which industry has the highest number of billionaires based on their continent"
format: html
editor: visual
execute:
  echo: false
---

#### Introduction and data

Our topic focus on the dataset "Billionaires" (2016), which contains information on the Billionaires in the world in 1996, 2001, 2014. The dataset involves information on each billionaire such as their country, wealth worth, wealth type, industry, etc. Using some of these variables, we came up with a question that helps us gather more insight on the wealth world, which is helpful for those who are deciding which industry to enter in North America, and how that changes over time.

Research Question and Hypothesis:

-   How has the relationship between wealth worth and industry among billionaires changed in North America as time goes on?

Based on our prior background knowledge, we predict that the number of billionaires involved in the industry of technology-computer will increase as time goes by because technology is an industry that is growing rapidly. We believe that the consumer industry may increase as well, and that the some of the more popular industries in 1996 might decrease in the number of billionaires as time passes. More broadly speaking, we hypothesize that the overall number of billionaires will increase, and therefore each industry will have a higher number of billionaires as time progresses, simply because there is more money in the world. We also predict that the average wealth worth will increase among all billionaires across industries as time goes.

The data was from the CORGIS Dataset Project, collected by Ryan Whitcombwas in 1996, 2001, and 2014. \[1\] We are using data from all three years to see how the wealth industries have changed over time by comparing data about the wealth industries from each provided year. It compiled Forbes World's Billionaires list and shows a record number of billionaires in the world while adding detailed information on the individuals listed. The relevant variables include the year, wealth worth, industry, and their continent. In total, the data set has 22 columns and 2614 observations. We are focusing our studies on the continent North America, to explore the relationship between billionaires and wealth worth in this area in particular over time.

To help us answer our research question, we looked at the Businesstech article, "The job sectors where billionaires make their money" presents findings from a study by UBS and PwC on the sectors where most billionaires succeeded. \[2\] The study analyzed the wealth of 2,000 billionaires worldwide and found that the top sectors where billionaires made their wealth are finance and investments, technology, manufacturing, real estate, and fashion and retail. Finance and investments had the most billionaires with 267, followed by technology with 221, manufacturing with 215, real estate with 163, and fashion and retail with 135. The study underscores the diversity of the sectors in which billionaires can generate wealth.

This article presents findings using billionaires from all over the world, whereas our research question is only exploring billionaires within North America. This will allow us to compare how the relationship between billionaires in North America and their industries differ from billionaires worldwide. Additionally, the article notes that technology is a top sector for billionaires to make most of their money, which reflects our hypothesis that technology will reflect the greatest increase in billionaires, as it is a sector that is growing rapidly.

#### Methodology

Our methodology involves multiple components. First, we found the number of billionaires per industry for each of the three years (1996, 2001, and 2014). Using this information, we can compare them and see how the number of billionaires has changed over time. Of course, this does not tell us anything about quantity of wealth, so in addition to the number of billionaires alone, we thought it would be beneficial to find the average wealth worth of the billionaires in each industry. We did this for all three years, and created a visualization to show how mean wealth worth has changed. From this, we can see the growth of certain industries as well as the diminish of others. Lastly, we conducted a hypothesis test for the general mean wealth worth, first for 2001 and 2014, and then for 1996 and 2001. These hypothesis tests tell us whether there was a true, significant change in mean wealth worth between those years. This is general, but could be done for the specific industries as well.

```{r}
#| label: load-pkgs
#| message: false

library(tidyverse)
library(tidymodels)
```

```{r}
#| label: load-data-2014
#| fig-width: 20
#| message: false

#Load data
billionaires <- read_csv("data/billionaires.csv")

df_1 <- billionaires|>
  dplyr::select(year, name, "wealth.worth in billions", wealth.how.industry, location.region, location.citizenship)|>
  rename_with(~'wealth.worth.billions', "wealth.worth in billions")|>
  mutate(continent = case_when(
    location.region == "Latin America" & location.citizenship == "Mexico" ~ "North America",
    TRUE ~ location.region
  ))
```

```{r}
#| label: count-billionaires-per-year

df_1996 <- df_1 |>
  filter(year == 1996, wealth.how.industry != 0) |>
  group_by(wealth.how.industry) |>
  summarize(num_billionaires = n()) |>
  arrange(desc(num_billionaires))
df_1996

df_2001 <- df_1  |>
  filter(year == 2001, wealth.how.industry != 0) |>
  group_by(wealth.how.industry) |>
  summarize(num_billionaires = n()) |>
  arrange(desc(num_billionaires))
df_2001

df_2014 <- df_1  |>
  filter(year == 2014, wealth.how.industry != 0) |>
  group_by(wealth.how.industry) |>
  summarize(num_billionaires = n()) |>
  arrange(desc(num_billionaires))
df_2014



```

```{r}
#| label: mean_wealth_1996

#Create data frame for mean wealth in 1996
df_1996 <- df_1 |>
  filter(year == 1996) |>
  filter(wealth.how.industry != 0) |>
  filter(location.region == "North America") |>
  group_by(wealth.how.industry) |>
  summarize(mean_wealth = mean(wealth.worth.billions, na.rm = T)) |>
  mutate(year = if_else(mean_wealth != 0, 1996, 0))
  

```

```{r}
#| label: mean_wealth_2001

#Create data frame for mean wealth in 2001
df_2001 <- df_1 |>
  filter(year == 2001) |>
  filter(wealth.how.industry != 0) |>
  filter(location.region == "North America") |>
  group_by(wealth.how.industry) |>
  summarize(mean_wealth = mean(wealth.worth.billions, na.rm = T))|>
  mutate(year = if_else(mean_wealth != 0, 2001, 0))
```

```{r}
#| label: mean_wealth_2014

#Create data frame for mean wealth in 2014
df_2014 <- df_1 |>
  filter(year == 2014) |>
  filter(wealth.how.industry != 0) |>
  filter(location.region == "North America") |>
  group_by(wealth.how.industry) |>
  summarize(mean_wealth = mean(wealth.worth.billions, na.rm = T))|>
  mutate(year = if_else(mean_wealth != 0, 2014, 0))
```

```{r}
#| label: visualization
#| fig-width: 10
#| fig-height: 8

#Assign color to the legend
distinct_colors <- c("#E6194B", "#3CB44B", "#FFE119", "#0082C8", "#F58231", "#911EB4", "#46F0F0", 
                     "#F032E6", "#D2F53C", "#008080", "#AA6E28", "#800000", "#000080", "#808000",
                     "#E6BEFF", "#AAFFC3", "black")

#Combine data frame together
df_rbind <- rbind(df_1996, df_2001)
df_rbind <- rbind(df_rbind, df_2014)

#visualize the graph
df_rbind |>
  ggplot(
    aes(x = year,
        y = mean_wealth,
        color = wealth.how.industry))+
  geom_line(size = 1) +
  geom_point() +
  scale_x_continuous(limits = c(1996, 2014.5), breaks = c(1996, 2001, 2014)) +
  theme_classic()+
  scale_color_manual(values = distinct_colors) +
  labs( title = "Mean Wealth Worth in Billions By Year Per Industry",
    x = "Year",
    y = "Mean Wealth Worth in Billions ($)",
    color = "Industry type"
  )

```

```{r}
#| label: data-frames-for-hypothesis-testing
df_2014 <- df_1|>
  filter(year == "2014")|>
  dplyr::select(wealth.worth.billions, wealth.how.industry)


df_2001<- df_1|>
  filter(year  == "2001")|>
  dplyr::select(wealth.worth.billions, wealth.how.industry)

df_1996<- df_1|>
  filter(year  == "1996")|>
  dplyr::select(wealth.worth.billions, wealth.how.industry)

```

$H_{0}= 2014-2001 \le 0$

$H_{a}= 2014 - 2001 > 0$

The null hypothesis states that from 2001 to 2014, the average wealth worth has not changed.

The alternative hypothesis states that from 2001 to 2014, the average wealth worth has increased.

```{r}
#| label: hypothesis-test
df_2014mean<- df_2014|>
  group_by(wealth.how.industry) |>
  summarize(mean_wealth = mean(wealth.worth.billions, na.rm = T))

df_2001mean<- df_2001|>
  group_by(wealth.how.industry) |>
  summarize(mean_wealth = mean(wealth.worth.billions, na.rm = T))


df2001mean_wealth_combined <- mean(df_2001mean$mean_wealth, na.rm = TRUE)

df2014mean_wealth_combined <- mean(df_2014mean$mean_wealth, na.rm = TRUE)

estimate <-3.429636 - 2.568625
```

```{r}
#| eval: False
df_1|>
  filter(!is.na(wealth.worth.billions), year == 2014)|>
  count(wealth.how.industry)

df_1|>
  filter(!is.na(wealth.worth.billions), year == 2001)|>
  count(wealth.how.industry)

sd1 <- df_2014|>
  summarize(sd_a = sd(wealth.worth.billions, na.rm = T)) |>
  as.numeric()
n1 <-1653

sd2 <- df_2001|>
  summarize(sd_a = sd(wealth.worth.billions, na.rm = T)) |>
  as.numeric()
n2 <-538

tscore <- (estimate - 0) / sqrt(((sd1^2)/n1) + ((sd2^2)/n2))
pt(tscore, df= 1171.399 , lower.tail = F)
```

```{r}
df_1996mean<- df_1996|>
  group_by(wealth.how.industry) |>
  summarize(mean_wealth = mean(wealth.worth.billions, na.rm = T))

df1996mean_wealth_combined <- mean(df_1996mean$mean_wealth, na.rm = TRUE)

estimate1<- 2.568625 - 2.335113
```

```{r}
#| eval: False
df_1|>
  filter(!is.na(wealth.worth.billions), year == 2001)|>
  count(wealth.how.industry)

df_1|>
  filter(!is.na(wealth.worth.billions), year == 1996)|>
  count(wealth.how.industry)

sd3 <- df_2001|>
  summarize(sd_a = sd(wealth.worth.billions, na.rm = T)) |>
  as.numeric()
n3 <-538

sd4 <- df_1996|>
  summarize(sd_a = sd(wealth.worth.billions, na.rm = T)) |>
  as.numeric()
n4 <-423

tscore <- (estimate1 - 0) / sqrt(((sd3^2)/n3) + ((sd4^2)/n4))
pt(tscore, df= 793.3797 , lower.tail = F)


```

#### Results

-   To answer our research question, we created a plot to visualize the relationship between industry and wealth worth, with industry being on the x-axis and wealth worth in billions on the y-axis. Additionally, in order to compare these variables by continent, we used facet wrap to make multiple plots next to each other. This visualization made it easy for us to draw conclusions to our question.

-   From the table depicting the number of billionaires per continent in 2014, we found that overall, North America had the most billionaires (as our hypothesis stated), followed by Europe and then Asia. This does not line up with the prediction, as we had predicted Asia to come first. For industry, we found that technology-computer was in fact the industry with the most billionaires in North America. However, it was found that each continent had a very different turn out regarding which industry was the most successful. For Europe and Latin America, the industry with the most billionaires was the consumer industry; for Africa, the diversified financial industry; and for Asia, the real estate industry.

**Limitations and future research:**

1.  Inflation: We did not consider the effects of inflation. Our model were based on the exact wealth worth in billion dollars in those years. We also anticipated that inflation can have a significant impact on wealth worth since 1996. We\'d recommend future research does take in effect of inflation into account.

2.  Heritage: Some billionaires in our data set were inherited from their parents. Therefore their data may not accurately reflect their industry type.

3.  Data from 1996, 2001, and 2014 are not enough for a comprehensive analysis. In order to form a more precise and accurate model, we\'d recommend to include more data from not just 3 years but every consecutive year from the beginning to the end so that a better trend can be presented.

**Citation and Reference**

\[1\] "Billionaires CSV File" from the CORGIS Dataset Project. By Ryan Whitcomb, Version 2.0.0, created on 5/17/2016.

\[2\] Businesstech. (2022, April 18). The job sectors where most billionaires make their money. Retrieved March 9, 2023, from<https://businesstech.co.za/news/business/576098/the-job-sectors-where-most-billionaires-make-their-money/>
